\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-24 WOOT/Files/related_work.tex

Besides attacking from the protocol perspective, there are works trying to use USB device as a payload delivery means. Duqu\cite{duqu} uses a user-mode rootkit to hide malicious files on the USB storage device and uses a zero-day exploit\cite{zero-day} to execute the malware automatically. There are also works like \cite{brain, stuxnet, conficker,flame} following the same paradigm and performing code-injection attacks. These attacks are much more damaging and flexible comparing to those previous ones, but they requires certain existing flaw like \cite{zero-day} and USB are merely a payload delivery method.

As a data transmission protocol, USB inevitably leaks electromagnetic signals to the environment which may contains sensitive information. Leveraging this physical phenomenon, there are works like \cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} eavesdropping leaked signals and recovering the sensitive data. In a similar fashion, \cite{usbkiller, cable, usbee, turnip} use the RF transmitter to inject signal to cause physical damage to the host machine. Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is too difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.

>>>>

Besides attacking from the protocol perspective, there are works trying to use USB device as a payload delivery means. Duqu\cite{duqu} uses a user-mode rootkit to hide malicious files on the USB storage device, \cite{flame} uses a zero-day exploit and malicious \textit{autorun.inf} to execute the malware automatically. There are also works like \cite{brain, stuxnet, conficker} following the same paradigm and performing code-injection attacks. These attacks are much more damaging and flexible comparing to those previous ones, but they requires certain existing flaw like \cite{zero-day} and USB are merely a payload delivery method.

As a data transmission protocol, USB inevitably leaks electromagnetic signals to the environment which may contains sensitive information. Leveraging this physical phenomenon, there are works like \cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} eavesdropping leaked signals and recovering the sensitive data. In a similar fashion, \cite{usbee, turnip} emit electromagnetic emissions by data injection on the bus with the connected USB devices as a RF transmitter and \cite{usbkiller, cable} inject analog power to cause physical damage to the host machine. Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is too difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
